---
title: "EMPLOYEE PROJECT"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
data <- read.csv("C:\\Users\\Prince\\Desktop\\Employee.csv")

```

#What is the distribution of educational qualifications among employees?

# Educational Qualifications distribution

```{r}
column_names <- colnames(data)
print(column_names)
```
```{r}
library(ggplot2)
educational_distribution <- ggplot(data, aes(x = Education)) +
  geom_bar(fill = "blue") +
  labs(title = "Distribution of Educational Qualifications",
       x = "Educational Qualification",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(educational_distribution)
```
#How does the length of service (Joining Year) vary across different cities?
```{r}
boxplot_plot <- ggplot(data, aes(x = City, y = JoiningYear)) +
  geom_boxplot() +
  labs(title = "Variation in Joining Year Across Cities",
       x = "City",
       y = "Joining Year") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(boxplot_plot)

```
#Is there a correlation between Payment Tier and Experience in Current Domain?
```{r}
anova_result <- aov(ExperienceInCurrentDomain ~ PaymentTier, data = data)
print(summary(anova_result))
```
# There is no correlation between Payment Tier and Experience in Current Domain. 

# What is the gender distribution within the workforce?
```{r}
library(ggplot2)
gender_distribution <- ggplot(data, aes(x = Gender)) +
  geom_bar(fill = "orange") +  # For a bar chart
  labs(title = "Gender Distribution Within the Workforce",
       x = "Gender",
       y = "Count") +
  theme_minimal()

print(gender_distribution)

```
```{r}
library(ggplot2)
leave_distribution <- ggplot(data, aes(x = LeaveOrNot)) +
  geom_bar(fill = "green") +
  labs(title = "Leave-Taking Behavior of Employees",
       x = "Leave Taken",
       y = "Count") +
  theme_minimal()

print(leave_distribution)
```



